Segmentation of Electron Microscopy Images for Connectomics

### 2018-05-02 papers/quals2018/1_compression.tex
paper: updated file names to match order

Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes.
Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
To encode the segment shapes, we consider the boundary pixels between two segments. 
Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment (Fig~\ref{fig:compression}, left). 
The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:

@@

Our compression scheme outperforms all existing methods.
We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and achieve ratios of $700\times$ on average.
We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim687\times$.

>>>>

Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes~\cite{matejek2017compresso}.
Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
To encode the segment shapes, we consider the boundary pixels between two segments. 
Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment (Fig~\ref{fig:compression}, left). 
The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:

@@

Our compression scheme outperforms all existing methods.
We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and together they achieve ratios of $920\times$ on average.
This outperforms existing strategies by over 80\%.
The fundamental principles guiding Compresso are valid for a diverse set of segmentation datasets and we improve on existing methods for MRI and image segmentation datasets. 
We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim687\times$.
